---
output:
  github_document:
    html_preview: FALSE
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# hello50

Author: _Noam Ross_

[![License: MIT](https://img.shields.io/badge/License-MIT-blue.svg){data-external="1"}](https://opensource.org/licenses/MIT)
[![Project Status: WIP - Initial development is in progress, but there has not yet been a stable, usable release suitable for the public.](http://www.repostatus.org/badges/latest/wip.svg){data-external="1"}](http://www.repostatus.org/#wip)
[![CircleCI](https://circleci.com/gh/noamross/hello50.svg){data-external="1"}](https://circleci.com/gh/noamross/hello50)
  [![AppVeyor build status](https://ci.appveyor.com/api/projects/status/github/noamross/hello50?branch=master&svg=true){data-external="1"}](https://ci.appveyor.com/project/noamross/hello50)
[![codecov](https://codecov.io/gh/noamross/hello50/branch/master/graph/badge.svg){data-external="1"}](https://codecov.io/gh/noamross/hello50)
[![CRAN status](https://www.r-pkg.org/badges/version/hello50){data-external="1"}](https://cran.r-project.org/package=hello50)

It does some stuff

## Installation

Install the **hello50** package with this command:

```{r install_me, eval = FALSE}
source("https://install-github.me/noamross/hello50")
```

```{r message=FALSE, warning=FALSE, error=FALSE, include=FALSE}
options(width=120)
```

## Usage

```{r example}
#library(hello50)

# some example code
```


# Current Verison

```{r version}
#packageVersion("hello50")
```

## Contributing

Want have feedback or want to contribute? Great! Please take a look at the [contributing guidelines](https://github.com/noamross/hello50/blob/master/.github/CONTRIBUTING.md) before filing an issue or pull request. 

Please note that this project is released with a [Contributor Code of Conduct](https://github.com/noamross/hello50/blob/master/.github/CODE_OF_CONDUCT.md). By participating in this project you agree to abide by its terms.
